\textbf{CPSC 504 Project\\\vspace{3 cm}\Huge{An investigation into an application to manage data transformations and updates}\vspace{2 cm}}

### 2015-04-08 Final_Paper/Paper.tex
This is the actual draft of the Introduction. =D

\documentclass[12pt]{article}
\begin{document}
\begin{titlepage}
\title{\textbf{CPSC 504 Project\\\vspace{3 cm}\Huge{An investigation into an application to manage data transformations and updates}\vspace{2 cm}}}
\date{\vspace{2 cm} April 14, 2015}

@@

\newpage
\section{Introduction}
The basis

>>>>

\documentclass[12pt]{article}
\usepackage{color}
\begin{document}
\begin{titlepage}
\title{\textbf{CPSC 504 Project\\\vspace{3 cm}\Huge{An investigation into an application to manage data transformations and updates}\vspace{2 cm}}}
\date{\vspace{2 cm} April 14, 2015}

@@

\newpage
\section{Introduction}
This project is built on top of the theoretical framework done in the M.Sc thesis of Arni Thrastarson \cite{arniThesis} and focuses on the first of the four scenarios detailed in the work. The first scenario is about trying to investigate how changes made by a data application can be captured and propagated to a remote data source. The main workflow of this scenario would be a remote (possibly third party) application pulling the data from a data source to use locally. The application will receive a local copy of the data along with a schema mapping to identify which tables the columns in the local copy of the data came from. A user using the application may notice inconsistencies with the data and go to correct it. The changes made by this user are logged in a transformation script and when the time comes to update the data source, the transformation script is sent to the data store and the changes detailed in the script are applied.

\noindent Our primary contributions are:
\begin{enumerate}
	\item{Using logical programming concepts to define a data transformation language that captures changes made to a relational data model}
	\item{Design decisions about how the relational model should react and handle schema changes}
	\item{A preliminary investigation into view maintenance policies for the remote datastore}
	\item{Further detailing the scenario in which an application views a subset of columns from one or more tables in a remote dataset}
	\item{Deciding which issues to assign to the server side and which to the client side}
\end{enumerate}
